
\documentclass[letterpaper,11pt,UTF8]{ctexart}
	%Linux Libertine
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage{xcolor}
\usepackage{framed}
\usepackage{libertine}
\usepackage{tocloft}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage[utf8]{inputenc}
\usepackage{tabularx}
\usepackage{enumerate}
\usepackage{helvet}
\usepackage{hyperref}\hypersetup{hidelinks}
\title{Taiyang-CV}
%-----------------------------------------------------------
%Edit these values as you see fit

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars


%-----------------------------------------------------------
%Margin setup

\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}
\setlength{\headheight}{30pt} 

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{8pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}
\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

 %   \usepackage{lmodern} 
\usepackage[top=0.75in,bottom=0.75in,right=0.75in,left=0.75in,headheight=30pt,headsep=1cm]{geometry}
\usepackage{fancyhdr}
\usepackage[english]{babel} % Required to compile in Windows
\usepackage[letterspace=150]{microtype}
\usepackage{fontspec}
%\setlength{\headheight}{110pt} %%or
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}
%\usepackage[headheight=500pt]{geometry}
\pagestyle{fancy}
%\lhead{Robert Lynch CV}
\fancyhead[L]{Curriculum Vitae -- TX}
%\fancyfoot[C]{Confidential}
%\fancyfoot[C] {\thepage}
 
\begin{document}

%\chead{Lynch CV}


\moveleft.5\hoffset\centerline{\LARGE\bf Taiyang XU / 徐太阳} % Your name at the top


 
\moveleft.5\hoffset\centerline{\large  Room 2104, Guanghua East Main Tower, Fudan University} % Your address
\moveleft.5\hoffset\centerline{\large  220 Handan Rd, Shanghai}
\moveleft.5\hoffset\centerline{\large  tyxu19 (YOU KNOW) fudan (DOT) edu (DOT) cn}
\moveleft.5\hoffset\centerline{\large  https://taiyangxu.github.io}
%-----------------------------------------------------------  



\vspace{3mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Employment}
\noindent \textbf{Fudan University / 复旦大学}\hfill Shanghai, China\\
\noindent{\quad}{\emph{Postdoctoral Researcher}} in the Department of Mathematics \hfill 2024 - Present\\
\noindent{{\qquad}Mentor: \href{https://lunzhangmaths.github.io}{\sl Lun Zhang}}
\vspace{3mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
%\flushright{\textbf {}}
\noindent \textbf{Fudan University / 复旦大学}\hfill Shanghai, China\\
\noindent{\quad}{\emph{Ph.D. in Mathematics}}\hfill 2019 - 2024\\
\noindent{{\qquad}Thesis: {\sl On the long-time asymptotics of the local and nonlocal mKdV equation under the nonzero background} / {\sl 非零背景下局域和非局域 mKdV 方程--解的长时间渐近分析} }\\
\noindent{{\qquad}Mentor: \href{https://math.fudan.edu.cn/fa/25/c30607a326181/page.htm}{\sl Engui Fan}}\\

\vspace{5mm} %5mm vertical space
\noindent\textbf{China University of Mining and Technology / 中国矿业大学}\hfill Xuzhou, Jiangsu Province, China\\
\noindent{\quad}{\emph{B.Sc. in Mathematics, Distinguished Honor}}\hfill 2015 - 2019\\
\noindent{{\qquad}Thesis: {\sl Inverse scattering theory and integrability on several kinds of nonlinear evolution equations} / {\sl 几类非线性发展方程的反散射方法及其可积性质的研究}}\\
\noindent{{\qquad}Thesis advisor: \href{https://faculty.cumt.edu.cn/SFTian/zh_CN/index.htm}{\sl Shoufu Tian}}
\vspace{3mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Research Interests}
\begin{flushleft}
Integrable PDEs, Random matrices theory, Determinantal point processes, 
Orthogonal polynomials, Asymptotic analysis, Riemann-Hilbert (RH) problems, Special functions, 
Painlev\'e equations.
\end{flushleft}
\vspace{3mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Research Articles}
\center
\large\textbf{Preprints}
\begin{flushleft}
    \begin{enumerate}[1.]
    \item Painlev\'{e} transcendents in the defocusing mKdV equation with non-zero boundary conditions (with Zhaoyu Wang and Engui Fan)\\
    (\href{https://arxiv.org/abs/2306.07073}{arXiv:2306.07073})

        
    \end{enumerate}
\end{flushleft}
\vspace{3mm}

\large\textbf{Publications in refereed journals}
\begin{flushleft}
    \begin{enumerate}[1.]
    \item Soliton resolution and asymptotic stability of $N$-soliton solutions for the defocusing mKdV equat-\\ion with finite density type initial data (with Engui Fan and Zechuan Zhang)\\ 
    {\bf To appear in Physica D}. \\
    (\href{https://arxiv.org/abs/2108.03650}{arXiv:2108.03650})

    \item Transient asymptotics of the modified Camassa-Holm equation (with Yiling Yang and Lun Zhang) \\
    {\bf Journal of the London Mathematical Society}, 110 (2024), e12967. \\
    (\href{https://londmathsoc.onlinelibrary.wiley.com/doi/10.1112/jlms.12967}{DOI: 10.1112/jlms.12967}) (\href{https://arxiv.org/abs/2308.06950}{arXiv:2308.06950})

    \item On the Cauchy problem of defocusing mKdV equation with finite density initial data: long-time asymptotics in soliton-less regions (with Engui Fan and Zechuan Zhang)\\
    {\bf Journal of Differential Equations}, 372 (2023), 55-122.\\
    (\href{https://www.sciencedirect.com/science/article/pii/S002203962300445X?via%3Dihub}{DOI: 10.1016/j.jde.2023.06.038}) (\href{https://arxiv.org/abs/2108.06284}{arXiv:2108.06284})

    \item Large-time asymptotics to the focusing nonlocal modified Kortweg-de Vries equation with step-like boundary conditions (with Engui Fan)\\
    {\bf Studies in Applied Mathematics}, 150 (2023), 1217-1273. \\
    (\href{https://onlinelibrary.wiley.com/doi/10.1111/sapm.12568}{DOI: 10.1111/sapm.12568}) (\href{https://arxiv.org/abs/2208.01268}{arXiv:2208.01268})

    \item Riemann-Hilbert approach for multisoliton solutions of generalized coupled fourth-order nonlinear Schr\"odinger equations
    (with Weiqi Peng and Shoufu Tian)\\
    {\bf Mathematical Methods in the Applied Sciences}, 43 (2020), 865-880.\\
    (\href{https://onlinelibrary.wiley.com/doi/10.1002/mma.5964}{DOI: 10.1002/mma.5964})
    \end{enumerate}
\end{flushleft}
\vspace{3mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Fellowships and Grants}
\begin{flushleft}
\begin{enumerate}[--]
\item Shanghai Post-doctoral Excellence Program, 2024--2026. / 上海市超级博士后项目. \\
``\textit{Riemann-Hilbert Method for Several Asymptotic Problems related to Universality from Integrable Systems and Random Matrix Theory}''  / ``\textit{可积系统和随机矩阵理论中若干渐近问题的普适性探索: 黎曼-希尔伯特方法}''\\
Role: Host / 主持

\item China Postdoctoral Science Foundation (Certificate No. 2024M760480), 2024-2026. / 中国博士后科学基金第76批面上资助.\\
``\textit{Semiclassical Asymptotics and Universality for Nonlinear Integrable Shallow Water Wave Systems}'' / ``\textit{非线性可积浅水波系统的半经典渐近与普适性}''\\
Role: Host / 主持
\end{enumerate}
\end{flushleft}
\vspace{3mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Teaching Activities}
\center
\begin{flushleft}
-- Spring, 2024: TA of Methods of Asymptotic Analysis (MATH630117), Fudan University.\\
-- Fall, 2021: TA of Calculus A (MATH120021.02), Fudan University.\\
-- Spring, 2020: TA of Calculus B (MATH120004.01), Fudan University (Online).\\
-- Fall, 2019: TA of Calculus B (MATH120003.01), Fudan University.
\end{flushleft}
\vspace{3mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Scholarships and Awards}
\center
\large\textbf{Doctorate}
\begin{flushleft}
    -- Graduation with Honors (Shanghai Outstanding Graduate), 2024. / 上海市优秀毕业生(研究生).\\
    -- Scholarship provided by Huatai Securities Technology, 2023. / 华泰证券科技奖学金.\\
    -- Scholarship provided by Pacific Insurance Company, 2022. / 太平洋保险奖学金.\\
    -- Outstanding Doctoral Candidate Scholarship provided by Fudan University, 2021. / 优秀博士候选人奖学金.\\
    -- Doctoral Scholarship of the Year provided by Fudan University, 2019-2023. / 博士生学年学业奖学金.
\end{flushleft}
\vspace{3mm}

\large\textbf{Undergraduate}
\begin{flushleft}
    -- Outstanding Undergraduates in China University of Mining and Technology, 2015-2019. / 中国矿业大学优秀毕业生.
\end{flushleft}
\vspace{3mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Seminars}
\center
\large\textbf{Seminars on Random Matrix Theory and Integrable Systems in Fudan during 2019--2026}
\begin{flushleft}
\small{\underline{(Here I only list the talks given by myself.)}}\\
-- \textit{Fredholm determinants from Schr\"odinger type equations, and deformation of Tracy-Widom distribution}, Oct, 2024.\\
-- \textit{Biorthogonal measures, polymer partition functions, and random matrices}, April, 2024.\\
-- \textit{Painlev\'e type asymptotics for the Camassa-Holm equation}, Oct, 2022.\\
-- \textit{A Riemann-Hilbert approach to Fredholm determinants of Hankel composition operators: scalar-valued kernels}, Sept - Oct, 2022.\\
-- \textit{Primitive potentials and bounded solutions of the KdV equation}, Sept, 2022.\\
-- \textit{Soliton V. The gas: Fredholm determinants, analysis and the rapid oscillations behind the kinetic equation}, May - June, 2022.\\
-- \textit{Airy kernel determinant solutions to the KdV equation and integro-differential Painlev\'e equations}, Dec, 2021 and Mar, 2022.\\ 
-- \textit{The defocusing nonlinear Schr\"odinger equation with step-like oscillatory initial data}, Oct, 2021.\\
-- \textit{Momenta spacing distributions in anharmonic and the higher order finite temperature Airy kernel}, Oct, 2021.\\
-- \textit{Long-Time behavior of the non-focusing nonlinear Schr\"odinger equation -- a case study}, April, 2021.\\
-- \textit{On the origins of Riemann-Hilbert problems in mathematics}, Nov, 2020 and Mar, 2021.
\end{flushleft}
\vspace{3mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Conferences \& Workshops}
\begin{flushleft}
\small{\underline{(\textcolor{red}{$^{*}$} indicates that I gave a talk.)}}\\
-- \textcolor{red}{$^{*}$}The 2nd Workshop on Integrable Systems and Random Matrix Theory 2025, Dongguan, China, 5-17 Jan, 2025.\\
-- \href{http://newton.kias.re.kr/~namgyu/index.html/Jeju24/}{Random Matrices and Related Topics}, Jeju island, Korea, 6-10 May, 2024.\\
-- \textcolor{red}{$^{*}$}\href{https://math.nbu.edu.cn/info/1084/6870.htm}{The 15th Hemudu Forum on Integrable Systems}, Ningbo, China, 24--26 Nov, 2023. \\
-- \href{https://focm2023.pages.math.cnrs.fr}{Foundations of Computational Mathematics 2023 (FoCM2023)}, Paris, France, 12--21 June, 2023.\\
-- \href{http://math.nbu.edu.cn/info/1084/3673.htm}{The 13rd Hemudu Forum on Integrable Systems}, Ningbo, China, 15 - 17 Oct, 2021.
\end{flushleft}	
\vspace{3mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Summer School}
\begin{flushleft}
    --  \href{https://sites.google.com/umich.edu/rmtschool/}{Random Matrix Summer School}, University of Michigan, Ann Arbor, USA, 17-28 June, 2024.
\end{flushleft}
\vspace{3mm}    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}